### 2011-12-20 joint action and knowing others minds/interacting mindreaders.2.tex
small fixes

\begin{abstract}
%Goal ascription is fundamental for mindreading.
What evidence grounds ascriptions of thoughts and actions,
and how does the evidence support the ascriptions?
In answering this question, 
philosophers sometimes ignore interaction and focus on mere observation.
The only evidence considered is 
evidence that would be available to mindreaders who observe their targets but are not necessarily in a position to interact with them.
The present paper identifies evidence 
that is available only to mindreaders capable of interacting with their targets.
Being poised to interact with others may enable one to know things about their minds which one might not otherwise be in a position to know.

@@

\section{Conclusion}
Our aim was to show that interaction benefits mindreading in this sense:
some routes to knowledge are closed to mindreaders who rely exclusively on observation
but
open to interacting mindreaders.
In pursuing this aim we focused on interactions which are joint actions.
Our suggestion was this.
Where an interpreter recognizes that her target is willing to engage in joint action
and is unwilling to change which goals her own actions will be directed to,
she may be in a position to know
that the goals of her target's actions will be her goals.
This in outline is the `your-goal-is-my-goal' route to knowledge.

To show that this route to knowledge is potentially valuable,
we argued that it enables interpreters to overcome two problems,
the problem of opaque means (section *)
and the problem of false belief (section *).
These problems may rarely arise for human adults thanks to sophisticated linguistic communication and extensive knowledge of how things can be achieved.  
But our focus has been on 
  very young humans,
  or other species,
  or earlier stages of evolution---%
on cases where there are 
  absent or fledgling communicative skills,
  limited insight into others' minds,
  and narrow knowledge of how things work.
Where this is the case,
the problems of false belief and opaque means may easily arise,
particularly in cases involving novel tools 
and 
communicative gestures.
In principle these interpreters 
could overcome the two problems 
by expliting your-goal-is-my-goal.
This demonstrates that 
expertise with 
  tools 
  and
  communicative gestures
does not presuppose rich insights into others intentions and beliefs.
It is consistent to suppose that 
such expertise,
far from  presupposing sophisticated forms of mindreading,
might instead
play a role in explaining their emergence in evolution or development (or both).

>>>>

\begin{abstract}
%Goal ascription is fundamental for mindreading.
What evidence grounds ascriptions of thoughts and actions,
and how does the evidence support the ascriptions?
In answering this question, 
philosophers sometimes ignore interaction and focus on mere observation.
The only evidence considered is 
evidence that would be available to mindreaders who observe their targets but are not necessarily in a position to interact with them.
The present paper identifies evidence 
that is available only to mindreaders capable of interacting with their targets.
Being able to interact with others may enable one to know things about their minds which one might not otherwise be in a position to know.
This matters for understanding possible roles for interaction in the evolution and development of mindreading.

@@

\section{Conclusion}
Our aim was to show that interaction can facilitate mindreading in this sense:
some routes to knowledge are closed to mindreaders who rely exclusively on observation
but
open to interacting mindreaders.
In pursuing this aim we focused on interactions which are joint actions.
Our suggestion was this.
Where an interpreter recognizes that her target is willing to engage in joint action
and is unwilling to change which goals her own actions will be directed to,
she may be in a position to know
that the goals of her target's actions will be her goals.
This in outline is the `your-goal-is-my-goal' route to knowledge.

To show that this route to knowledge is potentially valuable,
we argued that it enables interpreters to overcome two problems,
the problem of opaque means
and the problem of false belief.
These problems may rarely arise for human adults thanks to sophisticated linguistic communication and extensive knowledge of how things can be achieved.  
But interest in the evolution or development of mindreading
motivates focusing on 
interpreters with
  absent or fledgling communicative skills,
  limited insight into others' minds
  and narrow knowledge of how things work.
For such interpreters
the problems of false belief and opaque means may easily arise,
particularly in cases involving novel tools 
and 
communicative gestures.
Interpreters 
could overcome the two problems 
by exploiting the your-goal-is-my-goal route to knowledge.
It follows that 
expertise with 
  tools 
  and
  communicative gestures
does not presuppose rich insights into others' intentions and beliefs.
Such expertise,
far from  presupposing sophisticated forms of mindreading,
might instead
play a role in explaining their emergence in evolution or development (or both).
